When, why, and how to avoid, prefer, or tolerate inbreeding

### 2018-03-02 presentation/inbreeding.Rmd
More slides

## Individual interactions

<center>
![](images/ibm_general_1.png)
</center>

## Individual interactions

<center>
![](images/ibm_general_2.png)
</center>

## Individual interactions

<center>
![](images/ibm_general_3.png)
</center>

@@

## General modelling steps

>>>>

@@

## General individual-based model overview

<center>
![](images/ibm_steps_1.png)
</center>

<span style="font-size: 18px;">
Code [available on GitHub](https://github.com/bradduthie/PolyInbreed)
</span>

## General individual-based model overview

<center>
![](images/ibm_steps_2.png)
</center>

<span style="font-size: 18px;">
Code [available on GitHub](https://github.com/bradduthie/PolyInbreed)
</span>

## General individual-based model overview

<center>
![](images/ibm_steps_3.png)
</center>

<span style="font-size: 18px;">
Code [available on GitHub](https://github.com/bradduthie/PolyInbreed)
</span>

## General individual-based model overview

<center>
![](images/ibm_steps_4a.png)
</center>

<span style="font-size: 18px;">
Code [available on GitHub](https://github.com/bradduthie/PolyInbreed)
</span>

## General individual-based model overview

<center>
![](images/ibm_steps_4b.png)
</center>

<span style="font-size: 18px;">
Code [available on GitHub](https://github.com/bradduthie/PolyInbreed)
</span>

## General individual-based model overview

<center>
![](images/ibm_steps_5a.png)
</center>

<span style="font-size: 18px;">
Code [available on GitHub](https://github.com/bradduthie/PolyInbreed)
</span>

## General individual-based model overview

<center>
![](images/ibm_steps_5b.png)
</center>

<span style="font-size: 18px;">
Code [available on GitHub](https://github.com/bradduthie/PolyInbreed)
</span>

## General individual-based model overview

<center>
![](images/ibm_steps_6.png)
</center>

<span style="font-size: 18px;">
Code [available on GitHub](https://github.com/bradduthie/PolyInbreed)
</span>
